Viscous Transport in Eroding Porous Media

### 2019-07-31 docs/transport/erosion_transport.tex

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.38 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{\label{fig:NearWall} 
  A single body eroding in Stokes flow. The color indicates the shear
  stress on the body. Therefore, erosion is fastest in the yellow
  regions and slowest in the blue regions.  In this simulation, we use
  three minimum body-to-wall initial distances $d=h$ (left), $h/2$
  (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points
  on the body, a time step size of $\Dt=10^{-4}$, and smoothing
  parameters $\eps = 15/256$ and $\sigma=10/256$.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_vort}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_vort}
\includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
\caption{\label{fig:NearWall_vort} }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies initially placed in $[-1,1] \times
[-1,1]$.  The background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  We start by analyzing the effect of
erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\%  of the geometry eroded
bodies corresponding to a porosity of $0.38$.  As the bodies erode, the
area fraction decreases towards 0.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.  Starting around normalized
time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
which indicates that the flow rate can be written as a power law.  Using
a line of best fit, the flow rate is approximately \begin{align} U
\approx \left(\frac{t}{t_f}\right)^{15/4}, \end{align}
\todo[inline]{update this with whatever S-H gets} which is the dashed
line in Figure~\ref{fig:Eroding20flowrate}(b).

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.38 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{\label{fig:NearWall} 
  A single body eroding in Stokes flow. The color indicates the shear
  stress on the body in log scale. Therefore, erosion is fastest in the red
  regions and slowest in the blue regions.  In this simulation, we use
  three minimum body-to-wall initial distances $d=h$ (left), $h/2$
  (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points
  on the body, a time step size of $\Dt=10^{-4}$, and smoothing
  parameters $\eps = 15/256$ and $\sigma=10/256$.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_vort}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_vort}
\includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
\caption{\label{fig:NearWall_vort} The vorticity of the fluid with a single body eroding 
at time t=0.1001. The initial distances from body to wall are $h$ (left), $h/2$
  (middle), and $h/10$ (right).  }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies initially placed in $[-1,1] \times
[-1,1]$.  The background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  We start by analyzing the effect of
erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\%  of the geometry eroded
bodies corresponding to a porosity of $0.38$.  As the bodies erode, the
area fraction decreases towards 0.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.  Starting around normalized
time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
which indicates that the flow rate can be written as a power law.  Using
a line of best fit, the flow rate is approximately \begin{align} U
\approx \left(\frac{t}{t_f}\right)^{15/4}, \end{align}
\todo[inline]{update this with whatever S-H gets} which is the dashed
line in Figure~\ref{fig:Eroding20flowrate}(b).
